Adaptive Disk Storage for Interaction Graphs

### 2014-07-12 docs/graph-adapt/main.tex
added lp notes to paper

\While(\tcp*[f]{While storage exceeds threshold}){$H(\mathcal{P}, B) \geq
  \text{max}$}{
$\text{x}, \text{y}  \leftarrow  \closestPair{}  $\;
 $ \mathcal{P}(B)  \leftarrow \mathcal{P}(B) - x - y$ \;
  $\mathcal{P}(B)  \leftarrow \mathcal{P}(B)  + x \cup y$ \;
}
\Return $ \mathcal{P}(B)$  \tcp*{Final set of sub-blocks}
\end{algorithm}

@@

>>>>

\While(\tcp*[f]{While storage exceeds threshold}){$H(\mathcal{P}, B) \geq
  \text{max}$}{
$\text{x}, \text{y}  \leftarrow  \closestPair{}  $\;
 $ \mathcal{P}(B)  \leftarrow \mathcal{P}(B) - \{x, y\}$ \;
  $\mathcal{P}(B)  \leftarrow \mathcal{P}(B)  \cup \{ x \cup y \}$ \;
}
\Return $ \mathcal{P}(B)$  \tcp*{Final set of sub-blocks}
\end{algorithm}

@@

\subsection{Optimization}

\begin{enumerate}

   \item If an attribute is in a query:
\begin{alltt}
    v_a1_q1 = 1
    v_a2_q1 = 0
    v_a1_q2 = 0
    v_a2_q2 = 1
\end{alltt}

   \item If an attribute is in a partition:
\begin{alltt}
    v_a1_p1 = ?
    v_a2_p1 = ?
    v_a1_p2 = ?
    v_a2_p2 = ?
\end{alltt}

 \item If an partition is used by a query

\begin{alltt}
    v_p1_q1 = ?
    v_p1_q2 = ?
    v_p2_q1 = ?
    v_p2_q2 = ?
\end{alltt}

   \item If an attribute and partition are used by a query
\begin{alltt} 
   v_a1_p1_q1 = ?
    v_a1_p1_q2 = ?
    v_a2_p2_q1 = ?
    v_a2_p2_q2 = ?
\end{alltt}

    \item add constraint that all attributes must appear in a partition
\begin{alltt}
    v_a1_p1 + v_a1_p2  = 1
    v_a2_p1 + v_a2_p2 = 1
\end{alltt}

    \item the number of attributes use by query from a partition determines the
      value of \texttt{v\_p1\_q1} (either 0 or 1)
\begin{alltt}
    (v_a1_q1 * v_a1_p1 + v_a2_q1 
   * v_a2_p1) - v_p1_q1 >= 0
\end{alltt}

    \item To ensure that it is 0 or 1, we are going to add to the objective function, where K is some big value:
\begin{alltt}
   - K * v_p1_q1
   - K * v_p1_q2
   - K * v_p2_q1 
   - K * v_p2_q2
\end{alltt}

    \item add constraint to make sure that \texttt{v\_a1\_p1} and \texttt{v\_p1\_q1} determine
      \texttt{v\_a1\_p1\_q1}
\begin{alltt}
    v_a1_p1_q1 >= (v_a1_p1 + v_p1_q1) -1
\end{alltt}

    \item objective function : minimize the following, where the ?'s are constants

   \item Here is what we want:
\begin{alltt}
   (? * v_a1_p1_q1 + ? * v_a2_p1_q1 + ?)
  + (? * v_a1_p1_q2 + ? * v_a2_p1_q2 + ?)
  + (? * v_a1_p2_q1 + ? * v_a2_p2_q1 + ?)
  + (? * v_a1_p2_q2 + ? * v_a2_p2_q2 + ?)
\end{alltt}
\end{enumerate}
